Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-05 vesicle_code/docs/adhesion/adhesion.tex
added two-dimensional to intro

Boundary integral equation (BIE) approaches are well-suited for solving
the low Reynodls flow problems considered here as they lead to reduction
in dimensionality and achieve high-order accuracy even for moving
geometry problems. The BIE resolves the self-vesicle interaction using
quadrature for logarithmically singular integrands~\cite{alp1999}, but
as the vesicles adhere, the BIE solver must also resolve the
vesicle-vesicle {\em nearly-singular} hydrodynamic forces.  We use an
interpolation-based quadrature rule~\cite{qua-bir2014} to maintain
high-order accuracy for all vesicle-vesicle separation distances.  To
overcome the numerical stiffness induced by the membrane bending forces
and to control the global error, we employ a high-order spectrally
deferred implicit-explicit adaptive time stepping
scheme~\cite{quaife2016adaptive}.

This paper is organized as follows. In Section~\ref{sec:ge} we formulate
our model for vesicle hydrodynamics with adhesive interactions between
membranes of distinct vesicles.  We simulate the adhesion process of two
vesicles in a quiescent flow in Section~\ref{sec:qflow}, where we also
present a simple model to estimate how long it takes for two nearby
vesicles to reach an equilibrium configuration under adhesion. In
Section~\ref{sec:eflow} we numerically investigate the hydrodynamics of
a vesicle doublet in a fluid trap where the stagnation point is actively
controlled to be at the center of the vesicle doublet. From these
results we propose a novel application of the microfluidic fluid trap to
probe the adhesion strength between lipid bilayer membranes in
solutions. In Section~\ref{sec:sflow} we investigate how two vesicles
may form a doublet as they move toward each other under a planar shear
flow.  We map out the parameter regions for bound/unbound vesicles under
a planar shear flow, and we also investigate the effects of adhesive
interactions on the rheological properties of a dilute suspension of
vesicle doublets.  Finally in Section~\ref{sec:conclusions} we discuss
the implications of our results and point out a few potential future
directions.

>>>>

Boundary integral equation (BIE) approaches are well-suited for solving
the low Reynolds flow problems considered here as they lead to reduction
in dimensionality and achieve high-order accuracy even for moving
geometry problems. The BIE resolves the self-vesicle interaction using
quadrature for logarithmically singular integrands~\cite{alp1999}, but
as the vesicles adhere, the BIE solver must also resolve the
vesicle-vesicle {\em nearly-singular} hydrodynamic forces.  We use an
interpolation-based quadrature rule~\cite{qua-bir2014} to maintain
high-order accuracy for all vesicle-vesicle separation distances.  To
overcome the numerical stiffness induced by the membrane bending forces
and to control the global error, we employ a high-order spectrally
deferred implicit-explicit adaptive time stepping
scheme~\cite{quaife2016adaptive}.

This paper is organized as follows. In Section~\ref{sec:ge} we formulate
our model for two-dimensional vesicle hydrodynamics with adhesive
interactions between membranes of distinct vesicles.  We simulate the
adhesion process of two vesicles in a quiescent flow in
Section~\ref{sec:qflow}, where we also present a simple model to
estimate how long it takes for two nearby vesicles to reach an
equilibrium configuration under adhesion. In Section~\ref{sec:eflow} we
numerically investigate the hydrodynamics of a vesicle doublet in a
fluid trap where the stagnation point is actively controlled to be at
the center of the vesicle doublet. From these results we propose a novel
application of the microfluidic fluid trap to probe the adhesion
strength between lipid bilayer membranes in solutions. In
Section~\ref{sec:sflow} we investigate how two vesicles may form a
doublet as they move toward each other under a planar shear flow.  We
map out the parameter regions for bound/unbound vesicles under a planar
shear flow, and we also investigate the effects of adhesive interactions
on the rheological properties of a dilute suspension of vesicle
doublets.  Finally in Section~\ref{sec:conclusions} we discuss the
implications of our results and point out a few potential future
directions.
